A pipeline to analyse time-course gene expression data

### 2020-06-17 scripts/manuscript.Rmd
Adding a comment

```{r echo=FALSE}
contrasts[1:5]
```
**EAP**: I think it's better here to actually show the output, rather than a table, so you can see what the contrasts actually look like. I like to reserve table format for actual results, rather than code-like input

@@

**EAP** In fact, `which.min` which you used above, picks the first match, so actually a preference to assign into first cluster in this plot.

>>>>

```{r echo=FALSE}
contrasts[1:5]
```

@@

**EAP** In fact, `which.min` which you used above, picks the first match, so actually a preference to assign into first cluster in this plot.
**NV** Fair point… maybe this should be fixed somehow by adding a random
perturbation to the scores when the scores are equal? Although I think the
text is still appropriate: those genes should definitely be filtered out.
